A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 plots/cifar/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -8.7e+03 & -8.7e+03 & 0.83 & 0.84 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.83 & 0.84 & 0.02 & 0.02 & 0 & 0 \\
Log Logistic & -9.18e+03 & -9.18e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -9.43e+03 & -9.43e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -5.18e+03 & -5.19e+03 & 0.85 & 0.86 & 0 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.85 & 0.86 & 0.02 & 0.02 & 0 & 0 \\
Log Logistic & -5.42e+03 & -5.43e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -5.57e+03 & -5.58e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-09-11 plots/cifar100/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -4.39e+03 & -4.4e+03 & 0.81 & 0.8 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.81 & 0.79 & 0.01 & 0.01 & 0 & 0 \\
Log Logistic & -4.72e+03 & -4.73e+03 & 0.82 & 0.8 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -4.88e+03 & -4.88e+03 & 0.82 & 0.8 & 0 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR100 dataset.}
\label{tab:cifar100}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -1.79e+03 & -1.8e+03 & 0.81 & 0.81 & 0.01 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.8 & 0.81 & 0.03 & 0.02 & 0.02 & 0.01 \\
Log Logistic & -1.92e+03 & -1.93e+03 & 0.82 & 0.82 & 0.02 & 0.01 & 0.01 & 0 \\
Log Normal & -2.11e+03 & -2.12e+03 & 0.82 & 0.81 & 0.01 & 0.01 & 0.01 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-09-11 plots/mnist/aft_comparison.tex
update plots

\begin{table*}
\centering
\caption{Comparison of AFT Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -6.47e+03 & -6.48e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
Log Logistic & -6.48e+03 & -6.49e+03 & 0.91 & 0.91 & 0.04 & 0.04 & 0 & 0 \\
Log Normal & -6.62e+03 & -6.63e+03 & 0.9 & 0.91 & 0.03 & 0.03 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -6.46e+03 & -6.47e+03 & 0.9 & 0.9 & 0.01 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.9 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
Log Logistic & -6.47e+03 & -6.48e+03 & 0.91 & 0.91 & 0.04 & 0.04 & 0 & 0 \\
Log Normal & -6.61e+03 & -6.62e+03 & 0.9 & 0.91 & 0.03 & 0.03 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
